Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2016-10-27 manuscript.tex
latest

\usepackage{graphicx} 
%\usepackage{amsmath}
%\usepackage{a4wide}
%\usepackage{multicol,caption}
%\setlength{\textwidth}{16cm}
%\setlength{\textheight}{22cm}

@@

\section*{The Model}

@@

\section*{Results}

\subsection*{Mean Field Approximation}

@@

\subsection*{Invasion of rare genotypes and coexistence}\label{sec:invas}

@@

\subsection*{Environmental archetypes and Grime's triangle}

@@

How does Fig. 4 compare to Grime's C/S/R strategies? In disturbed environments, the ruderal (R) strategy is characterized by high fecundity, wide dispersal and short generation times.

We predict evolution for higher $b$, but not higher $c$ or lower $d$ (constrained to be large), amounts to focusing on fecundity. While there is no dispersal limitation in our model, propagules must be minimally effective at dispersal since our model only includes propagules which will enter territorial contests on unoccupied sites;

 Shorter generation times are thought to be a mechanism for increasing the chance that the reproductive cycle completes before disturbance-induced death

The evolution of the generation time itself is beyond the scope of our model, but it could

\section*{Discussion}

>>>>

\usepackage{graphicx} 
%\usepackage{a4wide}
%\usepackage{multicol,caption}
%\setlength{\textwidth}{16cm}
%\setlength{\textheight}{22cm}

@@

\section{Model}\label{sec:model}

@@

\section{Results}

\subsection{Mean Field Approximation}

@@

\subsection{Invasion of rare genotypes and coexistence}\label{sec:invas}

@@

\subsection{Grime's triangle}\label{sec:grime}

@@

How does Fig. 4 compare to Grime's C/S/R strategies? In disturbed environments, the ruderal (R) strategy is characterized by high fecundity, effective dispersal and rapid development to reproductive maturity. We predict evolution for higher $b$ and lower $d$, but not higher $c$. Higher $b$ means higher fecundity, and while our model does not account for differences in dispersal effectiveness, $b$ cannot be increased at the cost of poorer dispersal since $b$ represents only those propagules which end up contesting unoccupied territories. To some extent, lower $d$ could mean improved individual resistance to physical destruction, but it is hard to avoid the severe forms physical destruction that characterize the disturbance archetype. A more effective method to reduce $d$ is to shorten the time to reproductive maturity; this shortens the iteration time in our model and thereby reduces the chance of death per iteration $d$.

\section{Discussion}
